Analysis: The Sound of Teaching Music 1

### 2019-11-28 script/RNotebook/ioi.Rmd
tweak comments/description
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@

@@

### Plot
#### Bar graph
- Error bars show SEM of the mean

@@

##### Box plot
```{r ioi_art_order_all_box, echo = FALSE}
p_ioi_art_order_all_box <- ggplot(data = ioi_art_order, aes(x = Condition, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1) +
  geom_hline(yintercept = 188, linetype = "dashed") + # Tempo
  facet_wrap(Order ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Articulation") +
  theme(legend.position = "None")
p_ioi_art_order_all_box
```

@@

##### Box plot
```{r ioi_dyn_order_all_box, echo = FALSE}
p_ioi_dyn_order_all_box <- ggplot(data = ioi_dyn_order, aes(x = Condition, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1) +
  geom_hline(yintercept = 188, linetype = "dashed") + # Tempo
  facet_wrap(Order ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Dynamics") +
  theme(legend.position = "None")
p_ioi_dyn_order_all_box
```

>>>>

#### Plot
##### Line graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome (80bpm)

@@

#### Plot
##### Bar graph
- Error bars show SD of the mean
- A dashed line represents the tempo given by a metronome (80bpm)

@@

### Plot
#### Bar graph
- Error bars show SEM of the mean
- A dashed line represents the tempo given by a metronome (80bpm)

@@

```{r ioi_art_order_all_box, echo = FALSE}
p_ioi_art_order_all_box <- ggplot(data = ioi_art_order, aes(x = Condition, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1) +
  geom_hline(yintercept = 188, linetype = "dashed") + # Tempo
  facet_wrap(Order ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Articulation") +
  theme(legend.position = "None")
p_ioi_art_order_all_box
```

@@

```{r ioi_dyn_order_all_box, echo = FALSE}
p_ioi_dyn_order_all_box <- ggplot(data = ioi_dyn_order, aes(x = Condition, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1) +
  geom_hline(yintercept = 188, linetype = "dashed") + # Tempo
  facet_wrap(Order ~ .) +
  labs(y = "IOI (ms)", subtitle = "IOI: Dynamics") +
  theme(legend.position = "None")
p_ioi_dyn_order_all_box
```
